Tracing the Stellar Halo of Massive Galaxies to 100 kpc at $0.3<z<0.5$ using the Hyper Suprime-Cam

### 2017-05-25 draft/paper1_jenny.tex
Fig B1-3: Caption

%% ------------------------------------------------------------------------------------ %% 
    \begin{figure*}
        \begin{center}
        \includegraphics[width=\textwidth]{fig/redbcg_isedfit_example.pdf}
        \caption{
            Left: example output figure from \texttt{iSEDFit} that shows the SED 
        	fitting results. 
            The open-boxes show the observed fluxes in 5-band, and the solid, blue-dots
            show the best-fitted results, along with the high-resolution spectrum for
            this model reconstructed using the synthetic spectra from \texttt{FSPS}. 
            Top-left corner shows the best-fit stellar population parameters, and 
            bottom-right corner shows the ID, redshift of this object, and reduced 
            $\chi^2$ of the best-fit model.~~~
            Right: the Posterior distributions of a few key parameters.
            From top-left to bottom right are: 1) stellar mass (\logms{}); 2) age of the 
            population (mass and star-formation rate weighted) in Gyr; 3) star formation 
            rate ($\log\ \mathrm{SFR}\ (M_{\odot}/\mathrm{yr})$; instant one and the one 
            averaged over the previous 100 Myr; 4) stellar metallicity 
            ($\mathrm{Z}/\mathrm{Z}_{\odot}$); 5) dust extinction ($\mathrm{A}_V$ in mag);
            6) birthrate parameter ($\log\ b$; averaged over previous 100 and 1000 Myr).
            }
        \label{fig:ised}
        \end{center}
    \end{figure*}
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %% 
    \begin{figure*}
        \begin{center}
        \includegraphics[width=12cm]{fig/redbcg_isedfit_2.pdf}
        \caption{
            \song{Update the caption.}
            Relationships between \mstar{} and other stellar population 
            parameters using the results from \texttt{iSEDfit}. 
            The \textbf{left} figures are for the \rbcg{} sample, and the 
            \textbf{righ}t ones are 
            for the \nbcg{} sample. 
            They are both color-coded using the redshift of the object, while 
            their sizes reflect the magnitude differences in $i$-band between 
            the observed and best-fit value. 
            The four stellar population properties are: 
            1) \textbf{Top-left}: mass-weighted stellar age in Gyr; 
            2) \textbf{Bottom-left}: \m2l{} in $i$-band; 
            3) \textbf{Top-right}: mass-weighted stellar metallicity in unit of Solar 
            value;
            4) \textbf{bottom-right}: dust extinction values in magnitude.
            }
        \label{fig:ised_2}
        \end{center}
    \end{figure*}
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %% 
    \begin{figure}
        \begin{center}
        \includegraphics[width=\columnwidth]{fig/redbcg_isedfit_3.pdf}
        \caption{
            \song{Update the caption.}
            Comparisons of \mstar{} estimated by \texttt{iSEDFit} using different
            assumptions. 
            In each figure, we plot the \mstar{} from default model against their 
            differences with other models. 
            The top (bottom) row shows the comparisons of the \rbcg{} (\nbcg{}) sample. 
            The four models involved here are labeled as: 
            (A): default one; 
            (B): using the Salpeter IMF instead of the Chabrier one 
                (\textbf{Left column});
            (C): using the BC03 synthetic population model instead of the FSPS one
                (\textbf{Middle column});
            (D): assume that there is no dust extinction (\textbf{Right column}). 
            On each figure, the grey shaded region highlights the uncertainty 
            of the $\log($\logms{}$)$ using typical \mstar{} uncertainties from 
            both sides. 
            For each comparison, we highlight the median $\chi^{2}$ value, and the fraction
            of galaxies with $\chi^{2} > 10.0$ at the top. 
            We also show the histogram of the \mstar{}-differences on the right panel.
            }
        \label{fig:ised_3}
        \end{center}
    \end{figure}
%% ------------------------------------------------------------------------------------ %%

>>>>

%% ------------------------------------------------------------------------------------ %% 
    \begin{figure*}
        \begin{center}
        \includegraphics[width=\textwidth]{fig/redbcg_isedfit_example.pdf}
        \caption{
            \textbf{Left:} Example of output figure from \texttt{iSEDFit} that shows 
            the SED fitting results. 
            The open-boxes show the observed fluxes in 5-band, and the solid, blue-dots
            show the best-fitted results, along with the high-resolution spectrum for
            this model reconstructed using the synthetic spectra from \texttt{FSPS}. 
            Top-left corner shows the best-fit stellar population parameters, and 
            bottom-right corner shows the ID, redshift of this object, and reduced 
            $\chi^2$ of the best-fit model.~~~
            \textbf{Right:} the Posterior distributions of a few key parameters.
            From top-left to bottom right are: 
            1) stellar mass (\logms{}); 
            2) age of the population (mass and star-formation rate weighted) in Gyr; 
            3) star formation rate ($\log\ \mathrm{SFR}\ (M_{\odot}/\mathrm{yr})$; 
            instant one and the one averaged over the previous 100 Myr; 
            4) stellar metallicity ($\mathrm{Z}/\mathrm{Z}_{\odot}$); 
            5) dust extinction ($\mathrm{A}_V$ in mag);
            6) birthrate parameter ($\log\ b$; averaged over previous 100 and 1000 Myr).
            }
        \label{fig:ised}
        \end{center}
    \end{figure*}
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %% 
    \begin{figure*}
        \begin{center}
        \includegraphics[width=12cm]{fig/redbcg_isedfit_2.pdf}
        \caption{
            Relationships between \mstar{} and key stellar population parameters from 
            \texttt{iSEDfit}. 
            The four stellar population properties are: 
            1) \textbf{Top-left}: \mstar{}-weighted stellar population age in Gyr; 
            2) \textbf{Bottom-left}: SFR-weighted age in Gyr; 
            3) \textbf{Top-right}: \mstar{}-weighted stellar metallicity in unit of 
            Solar value;
            4) \textbf{bottom-right}: dust extinction value in $V$-band.
            As expected, most of the HSC massive galaxies are old, metal-rich, and 
            dust-free. 
            }
        \label{fig:ised_2}
        \end{center}
    \end{figure*}
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %% 
    \begin{figure}
        \begin{center}
        \includegraphics[width=\columnwidth]{fig/redbcg_isedfit_3.pdf}
        \caption{
            Comparisons of \mstar{} estimated by \texttt{iSEDFit} using different
            model assumptions. 
            In each figure, we plot the \mstar{} from the default model against the
            differences with other models. 
            The four models involved are labeled as: 
            (A): Default model; 
            (B): Using the Salpeter IMF instead of the Chabrier one 
                (\textbf{Top panel});
            (C): Using the BC03 synthetic population model instead of the FSPS one
                (\textbf{Middle panel});
            (D): No dust extinction (\textbf{Bottom panel}). 
            On each panel, the grey shaded region highlights the typical uncertainty 
            of the $\log($\logms{}$)$.            
            For each pair of models, we highlight their median $\chi^{2}$ values and 
            the fraction of galaxies with $\chi^{2} > 10.0$ at the top. 
            On each panel, we also show the histograms of the \mstar{}-differences on 
            the right side.
            }
        \label{fig:ised_3}
        \end{center}
    \end{figure}
%% ------------------------------------------------------------------------------------ %%
